Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
sec 4

A stable control system is known to have converging dynamics. 
Assume the closed-loop matrix eigenvalues are not repeated 
(which is sensible to do, since we select them). 
The trajectories distance from the reference point (in this case the origin) 
decreases over time within subspaces related to real-valued eigenvalues;  
however, this in general not the case when dealing with complex eigenvalues.  
Consider the closed-loop matrix, which updates the states every discrete time step, 
and select the eigenvalue with smallest (non-trivial) imaginary value -- call such value $\vartheta$. 
At every consecutive time steps $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
So taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
This $k$ is taken to be the completeness threshold.

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold for multi-staged verification.}
\label{fig:ct}
\end{figure*}

@@

We give the run-times required to synthesize a stable controller for all our
benchmarks. Here \textit{Benchmark} is the name of the employed
benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
to model the plant, while \textit{Time}
is the total time (in milliseconds) required to synthesize a stable controller
for the given plant, for CEGIS with multi-staged verification as well as
abstraction-based CEGIS. The precision for the controller,
$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.

>>>>

A stable control system is known to have converging dynamics. 
Assume the closed-loop matrix eigenvalues are not repeated 
(which is sensible to do, since we select them). 
The trajectories distance from the reference point (origin) 
decreases over time within subspaces related to real-valued eigenvalues;  
however, this in general not the case when dealing with complex eigenvalues.  
Consider the closed-loop matrix, which updates the states every discrete time step, 
and select the eigenvalue $\vartheta$ with smallest (non-trivial) imaginary value. 
At every consecutive time steps $kT_s, (k+1)T_s$, 
the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
So taking $k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
after $k{\leq}\overline{k}$ steps we have completed a full rotation, which results in a point closer to the origin, and it is the completeness threshold.

\begin{figure*}[t]
\centering
\includegraphics[width=0.6\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold for multi-staged verification.}
\label{fig:ct}
\end{figure*}

@@

We give the run-times required to synthesize a stable controller for each
benchmark in Table~\ref{tab:results}.  
Here \textit{Benchmark} is the name of the employed
benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
to model the plant, while \textit{Time}
is the total time (in milliseconds) required to synthesize a stable controller
for the given plant, for CEGIS with multi-staged verification as well as
abstraction-based CEGIS. The precision for the controller,
$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
